Interval Probability for Fuzzy Quantum Theories

### 2016-05-30 prob.tex
discreteGBKS.bib update citation...

To properly explain the previous example and generalize to arbitrary
quantum systems, we formally discuss projection operators and then
define a quantum probability space.

@@

\footnote{\yutsung{The definition of independence is interesting, and we
definitely need to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
theorem. However, the definition diverges. So we just leave it so far, and we
will go back if we really need it. (Maybe when discussing repeating
experiments?)}}

>>>>

To properly explain the previous example and generalize to arbitrary
quantum systems, we formally discuss projection operators, 
define quantum probability measures, and extend to quantum interval-valued
probability.

@@

\footnote{\yutsung{The definition of independence is interesting, and we
definitely need to discuss it when we want to discuss Bell's theorem and the Kochen-Specker
theorem. However, the definition diverges. So we just leave it so far, and we
will go back if we really need it in this paper. (Maybe when discussing repeating
experiments?)}}
